### 2013-12-18 manuscripts/dpp-msbayes/dpp-msbayes-figures.tex
Working on dpp ms.
In the process of integrating new figures into the text, and removing
old figures... A ways to go yet.

%% Validation accuracy
\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelDPP}
}{figValidationAccuracyDPPDPP}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelUniform}
}{figValidationAccuracyDPPUniform}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelOld}
}{figValidationAccuracyDPPOld}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelUshaped}
}{figValidationAccuracyDPPUshaped}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelDPP}
}{figValidationAccuracyUniformDPP}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelUniform}
}{figValidationAccuracyUniformUniform}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelOld}
}{figValidationAccuracyUniformOld}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelUshaped}
}{figValidationAccuracyUniformUshaped}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelDPP}
}{figValidationAccuracyOldDPP}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelUniform}
}{figValidationAccuracyOldUniform}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelOld}
}{figValidationAccuracyOldOld}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelUshaped}
}{figValidationAccuracyOldUshaped}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelDPP}
}{figValidationAccuracyUshapedDPP}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelUniform}
}{figValidationAccuracyUshapedUniform}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelOld}
}{figValidationAccuracyUshapedOld}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelUshaped}
}{figValidationAccuracyUshapedUshaped}

%% Validation model choice
\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelDPP}
}{figValidationModelChoiceDPPDPP}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelUniform}
}{figValidationModelChoiceDPPUniform}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelOld}
}{figValidationModelChoiceDPPOld}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelUshaped}
}{figValidationModelChoiceDPPUshaped}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelDPP}
}{figValidationModelChoiceUniformDPP}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelUniform}
}{figValidationModelChoiceUniformUniform}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelOld}
}{figValidationModelChoiceUniformOld}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelUshaped}
}{figValidationModelChoiceUniformUshaped}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelDPP}
}{figValidationModelChoiceOldDPP}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelUniform}
}{figValidationModelChoiceOldUniform}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelOld}
}{figValidationModelChoiceOldOld}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelUshaped}
}{figValidationModelChoiceOldUshaped}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelDPP}
}{figValidationModelChoiceUshapedDPP}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelUniform}
}{figValidationModelChoiceUshapedUniform}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelOld}
}{figValidationModelChoiceUshapedOld}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelUshaped}
}{figValidationModelChoiceUshapedUshaped}

%% Validation ordered models
\mFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationAccuracyDPPOrderedDPPOrdered}

\mFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationModelChoiceDPPOrderedDPPOrdered}

%% Power accuracy results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelDPP}
}{figPowerAccuracyExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelUniform}
}{figPowerAccuracyExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelOld}
}{figPowerAccuracyExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerAccuracyExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerAccuracyUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerAccuracyUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelOld}
}{figPowerAccuracyUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerAccuracyUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelDPP}
}{figPowerAccuracyOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelUniform}
}{figPowerAccuracyOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelOld}
}{figPowerAccuracyOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerAccuracyOldUshaped}

%% Power psi results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelDPP}
}{figPowerPsiExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelUniform}
}{figPowerPsiExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelOld}
}{figPowerPsiExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerPsiExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerPsiUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerPsiUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelOld}
}{figPowerPsiUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerPsiUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelDPP}
}{figPowerPsiOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelUniform}
}{figPowerPsiOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelOld}
}{figPowerPsiOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerPsiOldUshaped}

%% Power dispersion results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelDPP}
}{figPowerDispersionExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelUniform}
}{figPowerDispersionExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelOld}
}{figPowerDispersionExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerDispersionExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerDispersionUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerDispersionUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelOld}
}{figPowerDispersionUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerDispersionUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelDPP}
}{figPowerDispersionOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelUniform}
}{figPowerDispersionOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelOld}
}{figPowerDispersionOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerDispersionOldUshaped}

%% Power psi probability results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelDPP}
}{figPowerPsiProbExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelUniform}
}{figPowerPsiProbExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelOld}
}{figPowerPsiProbExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerPsiProbExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerPsiProbUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerPsiProbUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelOld}
}{figPowerPsiProbUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerPsiProbUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelDPP}
}{figPowerPsiProbOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelUniform}
}{figPowerPsiProbOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelOld}
}{figPowerPsiProbOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerPsiProbOldUshaped}

%% Power dispersion prob results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelDPP}
}{figPowerDispersionProbExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelUniform}
}{figPowerDispersionProbExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelOld}
}{figPowerDispersionProbExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerDispersionProbExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerDispersionProbUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerDispersionProbUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelOld}
}{figPowerDispersionProbUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerDispersionProbUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelDPP}
}{figPowerDispersionProbOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelUniform}
}{figPowerDispersionProbOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelOld}
}{figPowerDispersionProbOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerDispersionProbOldUshaped}

>>>>

%% Validation model choice
\mFigure{../../validation/images/validation-model-choice-psi.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsi}

\mFigure{../../validation/images/validation-model-choice-omega.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeDispersion < 0.01$}
}{figValidationModelChoiceOmega}

%% Power results
\mFigure{../../power-comparison/images/old-power-psi-4.pdf}{
    \powerCommentSummary{\powerSeriesOld}
    \powerPsiComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}

\mFigure{../../power-comparison/images/old-power-omega-4.pdf}{
    \powerCommentSummary{\powerSeriesOld}
    \powerDispersionComment{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}

\mFigure{../../power-comparison/images/old-power-psi-prob-4.pdf}{
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}

\mFigure{../../power-comparison/images/old-power-omega-prob-4.pdf}{
    \powerSupportCommentSummary{\powerSeriesOld}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
    Four of the six data-generating models of the \powerSeriesOld series
    are shown;
    please see Figure~S\ref{figPowerPsiOld} for all results.
}{figPowerPsiOld4}
